---
title: "Introduction to the `pimeta` package"
author: "Kengo Nagashima"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Introduction to the `pimeta` package}
  %\VignetteEncoding{UTF-8}
---

The `pimeta` package is easy.
Load your data and then pass it the `pima` function!
```{r, echo = TRUE, fig.width = 5, fig.height = 3}
library("pimeta")
library("ggplot2")
data(sbp, package = "pimeta")

# a parametric bootstrap prediction interval
piboot <- pima(
  y        = sbp$y,      # effect size estimates
  se       = sbp$sigmak, # within studies standard errors
  B        = 25000,      # number of bootstrap samples
  seed     = 14142135,   # random number seed
  parallel = 4           # multi-threading     
)
piboot
plot(piboot, base_size = 10, studylabel = sbp$label)
```

Several type of methods (`"HTS"`, `"HK"`, `"SJ"`, ...) are supported.
```{r, echo = TRUE}
# Higgins-Thompson-Spiegelhalter prediction interval
pima(sbp$y, sbp$sigmak, method = "HTS")
```

The `convert_bin()` function converts binary outcome data to effect size estimates and within studies standard errors vectors.
A data set of 13 placebo-controlled trials with cisapride that was reported by Hartung and Knapp (Stat Med., 2001, [doi:10.1002/sim.1009](https://doi.org/10.1002/sim.1009)) was analyzed below.
Estimated values on the logarithmic scale can be back-transformed to the original scale with the `trans` option.
```{r, echo = TRUE, fig.width = 5, fig.height = 3}
m1 <- c(15,12,29,42,14,44,14,29,10,17,38,19,21)
n1 <- c(16,16,34,56,22,54,17,58,14,26,44,29,38)
m2 <- c( 9, 1,18,31, 6,17, 7,23, 3, 6,12,22,19)
n2 <- c(16,16,34,56,22,55,15,58,15,27,45,30,38)
dat <- convert_bin(m1, n1, m2, n2, type = "logOR")
head(dat, n = 3)
pibin <- pima(dat$y, dat$se, seed = 2236067, parallel = 4)
print(pibin, digits = 3, trans = "exp")
binlabel <- c(
   "Creytens", "Milo", "Francois and De Nutte", "Deruyttere et al.",
   "Hannon", "Roesch", "De Nutte et al.", "Hausken and Bestad",
   "Chung", "Van Outryve et al.", "Al-Quorain et al.", "Kellow et al.",
   "Yeoh et al.")
plot(pibin, digits = 2, base_size = 10, studylabel = binlabel, trans = "exp")
```

Save a plot to PNG:
```{r, eval = FALSE}
png("forestplot.png", width = 500, height = 300, family = "Arial")
plot(piboot, digits = 2, base_size = 18, studylabel = sbp$label)
dev.off()
```
or
```{r, eval = FALSE}
p <- plot(piboot, digits = 2, base_size = 10, studylabel = sbp$label)
ggsave("forestplot.png", p, width = 5, height = 3, dpi = 150)
```
